Guided Proofreading of Automatic Segmentations for Connectomics

### 2017-03-08 paper/supplemental/architecture.tex
Supplemental.
James proof
Update supplemental material to include merge error pseudocode, training datasets table and GALA description.

\subsection{Limitations}
Guided proofreading works on 2D image sections. This enables error correction without a computationally expensive alignment process. However, the output requires an additional (block-)merging step prior to 3D analysis.

>>>>

\subsection{Merge Error Detection Pseudo Code}

\begin{algorithm}[H]
\caption{Merge Error Detection for a label \emph{l}}\label{code:mergeerror}
\begin{algorithmic}[1]
%\State{mergeErrors = []}
%\For{\emph{l} in $\forall$labels}
	\State{$l_d$ = \textbf{dilate}(\emph{l}, 20)}
	\State{invImage = \textbf{invert}(image)}
	\For{N iterations}
		\State{$s_1$, $s_2$ = \textbf{randomSeedsOnBoundary}($l_d$)}
		\State{wsImage = \textbf{watershed}(invImage, $l_d$, $s_1$, $s_2$)}
		\State{border = \textbf{border}(wsImage)}
		\State{$p$ = \textbf{rank}(border)}
		\State{$p_\text{merge}$ = $1-p$}	
	\EndFor
	\State{\textbf{find}(max $p_\text{merge})$}

\end{algorithmic}
\end{algorithm}

\subsection{Limitations}
Guided proofreading works on 2D image sections. This enables error correction without a computationally expensive alignment process. However, the output requires an additional (block-)merging step prior to 3D analysis. Several software packages exist for this purpose.

As described in Section~\ref{sec:addexp}, the guided proofreading classifier has to be retrained if used on a different species than mouse. In our experiments, parameters did not need to be changed.

\section{Automatic Segmentation Pipeline}

We create a dense automatic segmentation of electron microscopy data using a combination of a U-net~\cite{RonnebergerFB15} and the GALA agglomeration method~\cite{nunez2014graph}. These classifiers are trained on different data than GP (Tab.~\ref{tab:trainingdata}).

\begin{table}[h]
\caption{Training data of membrane detection (U-Net / GALA) vs.~training data of GP vs.~test data.}%While the training of our classifier is more expensive, testing accuracy is superior. }
\vspace{-1mm}
\resizebox{\linewidth}{!}{
\begin{tabular}{lrrrr}
\toprule
%Dataset & \makecell{Training Set\\Membrane Detection (U-Net)} & \makecell{Training Set\\Guided Proofreading} \\ 
\makecell{Training Set\\U-Net / GALA} & \makecell{Training Set\\GP} & \makecell{Test Set\\GP}\\ 
\midrule
\makecell{AC3+AC4\\($1024\times1024\times175$vx)} & \makecell{L. Cylinder\\($2048\times2048\times250$vx)} &
\makecell{$\text{L. Cylinder}_\text{test}$\\($2048\times2048\times50$vx)}
\\ 
\makecell{AC4 excl. test\\ ($1024\times1024\times90$vx)} &  \makecell{L. Cylinder\\($2048\times2048\times250$vx)} &
\makecell{$\text{AC4}_\text{test}$ subvolume\\($400\times400\times10$vx)} \\ 
\makecell{AC3+AC4\\($1024\times1024\times175$vx)} & \makecell{CREMI A/B/C\\($1250\times1250\times300$vx)} &
\makecell{$\text{CREMI A/B/C}_\text{test}$\\($1250\times1250\times15$vx)} \\ 
\bottomrule
\end{tabular} 
}
\label{tab:trainingdata}
\end{table}

GALA uses a random forest classifier to agglomerate segments. We use an agglomeration level of 0.3 (after a grid search). Further details of our pipeline are described in~\cite{rhoananet}.
